Authors Response to Reviewer Comments

### 2023-09-22 manuscript/review/authorsResponse.qmd
Some suggestions for R Comments 1-5. More to follow on monday.

Thank you for pointing

@@

@@

>>>>

Thank you for pointing this out. We also discussed terminology several times and we agree. We followed your suggestion replaced 'regeneration' with 'recruitment' where the difference is not clear. However, we believe that in some places regeneration is more accurate. Especially in many parts of the introduction and discussion. We argue that regeneration is often only modeled via "recruitment", but with the aim to simulate the whole process of regeneration. In this context it makes more sense to use the general term (e.g., for discussion consequences.)

COMMENT from YK: I would argue that recruitment is evidence for successful regeneration. This allows us to use recruitment for discussions observation vs. simulation in both aspects: technical (recruitment) and general (regeneration).

@@

SUGGESTION YK: We understand the necessity of a clear statement in this regard. Reformulate by replacing "capture" with "do a good job in capturing" after models [L67].

@@

SUGGESTION YK: I think the paragraph can be simplified by dissentangling the issues and the corresponding approaches to resolve them. I suggest to resolve this comment with changing the text something like:

A focus on the modeling of tree regeneration processes is sorely
needed and overdue [@price2001; @walck2011] if we are to make reliable
projections of future forest dynamics, i.e., when the models need to be
operated in extrapolation mode, as well as from a fundamental ecological
point of view for increasing systems understanding. 
Tree regeneration has often been overlooked in previous research [@hanbury-brown2022] because of the challenges induced by trade offs between the spatial and temporal scales on which processes of regeneration act and the availability of data needed to analyse these processes [@clark1999].
Data on forest regeneration data are often fragmented,
which constitutes a major problem for model building [@clark1999].
For example monitoring on permanent plots (such as National Forest
Inventories) often measures tree regeneration with a design that captures the rate after the stand initiation phase [@hallsby2015; @zell2019]; Data from permanent plots, although available across
regions, are highly heterogeneous, rendering their use difficult in a
modeling context [@käber2021]; and targeted studies to
measure tree regeneration on experimental sites are often limited in
spatial extent, species studied, or the sub-set of processes that are
targeted [@berdanier2016; @collet2006].
